### 2015-01-07 paper/paper.tex
autocommit 01/07 16:25

\documentclass{jsarticle}
\renewcommand{\labelenumii}{\theenumii}
\renewcommand{\theenumii}{\theenumi.\arabic{enumii}.}
\usepackage[dvipdfmx,hiresbb]{graphicx}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algorithmic}
\begin{document}

@@

\begin{algorithm}                      
\caption{PBNF search framework}         
\label{alg1}                          
\begin{algorithmic}                  
\while {there is an nblock with open nodes}
\STATE lock; $b \leftarrow$ best free nblock; unlock
\while {$b$ is no worse than the best free nblock or we've done fewer than $m$ expansions}
\STATE $n \leftarrow$ best open node in $b$

\ENDWHILE
\ENDWHILE
\end{algorithmic}
\end{algorithm}

>>>>

\documentclass{jsarticle}
\renewcommand{\labelenumii}{\theenumii}
\renewcommand{\theenumii}{\theenumi.\arabic{enumii}.}
\usepackage[dvipdfmx,hiresbb]{graphicx}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algorithmic}
\captionsetup[algorithm]{labelformat=empty}
\begin{document}

@@

\begin{algorithm}                      
\caption{PBNF search framework}         
\label{alg1}                          
\begin{algorithmic}                  
\WHILE {there is an nblock with open nodes}
	\STATE lock; $b \leftarrow$ best free nblock; unlock
	\WHILE {$b$ is no worse than the best free nblock or we've done fewer than $m$ expansions}
		\STATE $n \leftarrow$ best open node in $b$
		\IF $f(n) > f(incumbent)$, prune all open nodes in $b$
		\ELSIF $n$ is a goal
			\STATE $incumbent \leftarrow n$
		\ELSE for each child $c$ of $n$
			\STATE insert $c$ in the open list of the appropriate nblock
\ENDWHILE
\ENDWHILE
\end{algorithmic}
\end{algorithm}
